\bf\mftitle

### 2011-03-01 doc/jInfer/xsdimport/xsdimport.tex
3187368 - Review documentation: cleanup - xsdimport done

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Robert Smetana \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & listed for each module separately \\ \hline
Public packages:       & listed for each module separately \\ \hline
\end{tabular}

@@

Similar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
\code{XSDProcessor} registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion if necessary (see \cite[section 4]{basiciggdoc}).

@@

\noindent This module implements the import functionality using API of a standard SAX parser. Its structure is divided in two packages. Package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax} holds the main parsing logic, while package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax.utils} contains two utility classes. Both \code{SAXAttributeData} and \code{SAXDocumentElement} serve as wrappers for tag attributes and tags of the input Schema file during parsing, to ease the process of extracting data from them.

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Robert Smetana \\ \hline
Required tokens       & none \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & listed for each module separately \\ \hline
Public packages       & listed for each module separately \\ \hline
\end{tabular}

@@

Similar to the \code{Processor} implementations in the \code{BasicIGG} module, this is the core class of \code{XSDImporter} logic.
\code{XSD\.Pro\.cessor} registers itself into \emph{schema} input folder, \emph{xsd} file extension and declares it cannot handle other file extensions.\\
Class depends on NBP lookups (see \cite[section 4.1]{archdoc}) to find available parsers, and uses the selected parser to perform the import operation on defined files.
Initial grammar generated by this processor is considered \emph{complex} and should be followed by expansion if necessary (see \cite[section 4]{basiciggdoc}).

@@

\noindent This module implements the import functionality using API of a standard SAX parser. Its structure is divided in two packages. Package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax} holds the main parsing logic, while package \code{cz.cuni.mff.ksi.jinfer.xsdimportsax.utils} contains two utility classes. Both \code{SAXAttributeData} and \code{SAX\.Do\.cu\.ment\.Ele\.ment} serve as wrappers for tag attributes and tags of the input Schema file during parsing, to ease the process of extracting data from them.
